Peer-graded Assignment: Reproduciable Data Project 1
====================================================

Set working directory
```{r}
setwd("/Users/sagashin/Desktop/Coursera_R_DS/Reproduciable")
```

Code for reading in the dataset and/or processing the data
```{r}
df <- read.csv("activity.csv")
df$date <- as.Date(df$date)
df <- df[!is.na(df$steps),]
```

Histogram of the total number of steps taken each day
```{r}
library(ggplot2)
library(dplyr)

hd <- df %>% 
        group_by(date) %>% 
        summarise(total_steps = sum(steps))

hist(hd$total_steps, col = "blue")
```

Mean and median number of steps taken each day
```{r}
smean <- mean(df$step, na.rm = TRUE)
smed <- median(df$step, na.rm = TRUE)
stats1 <- c(smean,smed)
names(stats1) <- c("mean","median")
stats1
```

Time series plot of the average number of steps taken
```{r}
mean1 <- tapply(df$step, as.factor(df$interval),mean)
name1 <- as.integer(names(mean1))
plot(name1,mean1,type="l", col = "red")
```
The 5-minute interval that, on average, contains the maximum number of steps
```{r}
df2 <- as.data.frame(mean1)
max <- max(df2$mean1)
df2[df2$mean1 == max,]
```
Code to describe and show a strategy for imputing missing data use mice package to impute
```{r}
library(mice)
```
read csv
```{r}
df3 <- read.csv("activity.csv")
```
impute date
```{r}
imp <- mice(df3)
```
complete dataset with imputed values
```{r}
comp <- complete(imp,2)
```
Histogram of the total number of steps taken each day after missing values are imputed
```{r}
chd <- comp %>% 
        group_by(date) %>% 
        summarise(total_steps = sum(steps))

hist(chd$total_steps, col = "blue")
cmean <- mean(comp$step, na.rm = TRUE)
cmed <- median(comp$step, na.rm = TRUE)
stats2 <- c(cmean,cmed)
names(stats2) <- c("mean","median")
```
mean and median for imputed dataset
```{r}
stats2
```
mean and median for non-imputed dataset
```{r}
stats1
```
Panel plot comparing the average number of steps taken per 5-minute interval across weekdays and weekends
```{r}
comp$date <- as.Date(comp$date)
wkd <- weekdays(comp$date) != c("土曜日","日曜日")
wke <- weekdays(comp$date) == c("土曜日","日曜日")
```
add a new column containing day of week
```{r}
comp$weekday = weekdays(comp$date)
```
add a new column containing either Weekday OR Weekend
```{r}
comp$weekday.type <- ifelse(comp$weekday == "土曜日" | comp$weekday == 
                                       "日曜日", "Weekend", "Weekday")
```
convert column to factor
```{r}
comp$weekday.type <- factor(comp$weekday.type)
```
Calculate mean steps by weekdays and weekend
```{r}
library(ggplot2)
library(dplyr)
sd <- comp %>% 
        group_by(interval,weekday.type) %>% 
        summarise(ms = mean(steps))
qplot(interval,ms,data = sd, facets = . ~ weekday.type, geom = "line", color = weekday.type,
      ylab = "Average Step")
```

All of the R code needed to reproduce the results (numbers, plots, etc.) in the report